An Empirical Analysis of the Role of Energy in Economic Growth

### 2014-04-21 Article/EconGrowth2.Rnw
Added microtype package.
Now the article (EconGrowth2.Rnw) loads the original models.

\usepackage{wrapfig}  % Allows wrapping of text around figures
\usepackage{soul}     % Provides strikethrough text
\usepackage{float}    % Allows precise positioning of tables and figures within the text
\usepackage{amsmath}  % Allows \begin{equation*} \end{equation*} for unnumbered equations
\usepackage{multirow} % To create multirow tables
\usepackage{hyperref} % To create hyperlinks in the paper

@@

# In Rstudio, this paper is generated from it's directory, which is "Article".
# We need to define paths relative to the location of the paper. 
# Relative path to historical data from Article
baseHistorical <- file.path("..", "data")
# We also need to define a directory path to the resample data results from "Article"
baseResample <- file.path("..", "data_resample")
@

>>>>

\usepackage{wrapfig}    % Allows wrapping of text around figures
\usepackage{soul}       % Provides strikethrough text
\usepackage{float}      % Allows precise positioning of tables and figures within the text
\usepackage{amsmath}    % Allows \begin{equation*} \end{equation*} for unnumbered equations
\usepackage{multirow}   % To create multirow tables
\usepackage{hyperref}   % To create hyperlinks in the paper
\usepackage{microtype}  % produces hanging punctuation and beautiful type

@@

# In Rstudio, this paper is generated from it's directory, which is "Article".
# We need to define paths relative to the location of the paper. 
# Relative path to historical data from Article
baseHistorical <- file.path("..", "data")
# We also need to define a directory path to the resample data results from "Article"
baseResample <- file.path("..", "data_resample")

# Load the fits to the original historical data
# This object should be passed in to functions that need specific fits.
oModels <- readRDS(file=file.path(baseResample, "oModels.Rdata"))
@
